\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-18 WOOT/Files/related_work.tex
wuhu

\subsection{USB Defence Security}
There are already some defense measures against BadUSB attacks. 
And there has been a comprehensive investigation of previous work.\cite{sok}.
BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
without these special pins, data can't be transferred in the USB cable. USB condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the usb device and host.
However, this method poses a great challenge to ease of use, and once deployed, it will block all USB-supported advanced functions other than charging. Pham et al. \cite{pham2010optimizing}, Metascan \cite{OPSWAT} and odix\cite{OLEA} provide scanning function for files on portable USB devices, and can prevent malicious code from BadUSB devices from attacking host.
There are also some work like TMSUI\cite{yang2015tmsui} USB
Unix Smart Blocker\cite{diwan2014complete}, which based on the unreliable information provided during USB device enumeration to defend against BadUSB.

Since USB devices may hide their real functionality from the user. GoodUSB\cite{tian2015defending} will report the functionality and identity information of the device to the user before the enumeration is completed. The user needs to explicitly specify the target functionality of the device. On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage. This restricts the device from loading only the drivers allowed by the user, but does not prevent the device from using available drivers to attack. For example, a malicious keyboard can type commands without the user's knowledge after enumeration. Because from the user's perspect, he must permit a USB-based keyboard the corresponding drivers to allow users to use keyboard to type, but once the drivers are loaded, the malicious usb-based keyboard may also automatically type commands. What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic eqxecution of malicious code.

Windows Defender ATP\cite{windenfenderwhite} can maintain a white list of USB devices, user can  only if one USB device is in the white list can it interact with host. This prevents all interactions between untrusted devices and the host. But this reduces the ease of use and requires users to have a certain safety awareness. For example, a naive user may add the USB device he found outdoors to his whitelist without precautions. Mohammadmoradi et al\cite{mohammadmoradi2018making} generate unique fingerprint based on the features and functions of the USB device, thereby building a whitelist of USB devices.

Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyze temporal characteristics of BadUSB-like attacks. This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, and can only inject instructions in a very short time to prevent the user from discovering. This causes the typing characteristics of BadUSB devices to be detected.

>>>>

\subsection{USB Defence Security}
There are already some defenses against BadUSB attacks. 
And there has been a comprehensive investigation of previous work.\cite{sok}.
BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
without these special pins, data can't be transferred in the USB cable. USB condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the usb device and host. At this case, `D-' and `D+' are disabled.
However, this method poses a great challenge to ease of use, and once deployed, it will block all USB-supported advanced functions other than charging. Pham et al. \cite{pham2010optimizing}, Metascan \cite{OPSWAT} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code over malicious devices from attacking host.
There are also some work like TMSUI\cite{yang2015tmsui} USB
Unix Smart Blocker\cite{diwan2014complete}, which based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.

Since USB devices may hide their real functionality from the user. GoodUSB\cite{tian2015defending} will report the functionality and identity information of the device to the user and the user needs to explicitly specify the target functionality of the device. On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage. This restricts the device from loading only the drivers allowed by the user, but does not prevent the device from using available drivers to attack. For example, a malicious keyboard can type commands without the user's knowledge after enumeration. Because from the user's perspect, he must permit a USB-based keyboard the corresponding drivers to allow himself to use keyboard to type, but once the drivers are loaded, the malicious usb-based keyboard can also automatically type commands. What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic eqxecution of malicious code.

Windows Defender ATP\cite{windenfenderwhite} can maintain a white list of USB devices, only if one USB device is in the white list can it interact with host. This prevents all interactions between untrusted devices and the host. But this reduces the ease of use and requires users to have a certain safety awareness. For example, a naive user may add the USB device he found outdoors to his whitelist without precautions. Mohammadmoradi et al\cite{mohammadmoradi2018making} generate unique fingerprint based on the features and functions of the USB device, thereby building a whitelist of USB devices.

Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyze temporal characteristics of BadUSB-like attacks. This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, so that the malicious device can only inject instructions in a very short time to prevent the user from discovering. This causes the typing characteristics of BadUSB devices to be detected.
